A generalized model for the charge transport properties of dressed quantum Hall systems

### 2021-11-19 response/response.tex

Thank you very much for your effort in managing the review process of our manuscript. We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received. Additionally, the subsequent sections of this document discuss the reviewer comments and our responses to them.

Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers. Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Red} red}.

\subsection*{General changes to the manuscript}

We have made some minor changes in language and presentation to improve the clarity and organization of the manuscript.
\begin{itemize}
    \item Section I - seventh paragraph (page 2): \\
        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
    \item Section VI - fourth paragraph (page 8): \\
        {\color{Red} Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
    \item Section VIII - first paragraph (page 10): \\
        {\color{Red} Finally, we derived analytical expressions for the diagonal components of the electric conductivity tensor concerning the 2DEG quantum Hall system operates at low temperatures.}
\end{itemize}

@@

We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work. We have considered all of your suggestions seriously and revised our manuscript as described below.

\subsubsection*{Comment 1 -
\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem. It has a minimal connection to realistic two-dimensional electron systems. The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance. Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}

We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices. Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance. First, we added a detailed comparison between our theoretical results and experiment observations when no radiation is present.  We also added a new section (Section VII) on this very aspect.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  The gate voltage modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations against our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
  \item Section VII (page 9):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

@@

  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.

  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig. 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

@@

  \item
  the applied microwave radiation power on the MIRO experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range. However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis. This leads us to recognize the formation of Floquet states together with conventional Landau levels. As we mentioned in our results, we used dressing high-intensity electromagnetic fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
  \item
  these fascinating MIROs are only observed under the influence of weak magnetic fields ($B < \SI{0.2}{\tesla}$) in experiments performed in Refs. \cite{zudov01,mani02,zudov03,mani04}. In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only with high-intensity magnetic fields. In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics. Therefore in our analysis, we aim at the effects induced by higher intensity magnetic fields ($B \sim \SI{1}{\tesla}$) than the MIRO experiments.

@@

Yes, indeed, experiments on quantum hall systems subject to a strong dressing field show elevated temperatures. However, as demonstrated in previous studies by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, it is possible to maintain low system temperature by limiting the dressing field to narrow pulses.

Although we have restricted our general derivation given in Eq.~[31] into a particular instance for comparison, there is no fundemental restriction in extending our theoretical model into different types of particle distribution functions. As presented in the previous work of Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.

@@

Suppose we apply an arbitrary directional polarized dressing field. In that case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis. This would change the amplitude of the associated dressing field ($E$) in each direction. There will be a new component in parallel to the conductivity component of interest, which will modify the time-dependent Hamiltonian given in Eq.~[2]. Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system. These will define the effect on the inverse scattering time matrix components. As mentioned in Ref. \cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states. The properties of these states depend on the characteristics of the applied dressing field. Therefore, the polarization method also changes the behavior of the Floquet states. These polarization-dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. However, in a dressed quantum Hall system with a $y$-directional linear polarized field, we predict the same longitudinal conductivity behaviors in diagonal components of the conductivity tensor.

@@

We want to thank the reviewer for his/her insightful comments on our work. To address your comments, we had to add new materials and reorganize our text. As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis. We hope our response and the corresponding changes we incorporated into the manuscript will be sufficient to clarify the issues raised.

\subsubsection*{Comment 1 -
\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case. I would like to see detailed analysis of how Figs 4 and 5 compare with available
experimental data. Without this addition, physical relevance of such
detailed calculations is questionable.
}

We thank the reviewer for pointing out the importance of this fact. In the revised manuscript, we have included a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  The gate voltage modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations against our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
\end{itemize}

@@

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

We omitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system. Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well. As mentioned in the work of Endo \textit{et al.} \cite{endo09}, within the magnetic field range of interest, the undressed
magneto-transport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects. Our work is very similar to theirs with an additional dressing field. Our results for the undressed system agree with the results in Ref. \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks. We have added this clarification in the manuscript.

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Red}
  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions. These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g see Endo \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - first paragraph (page 10):\\
  {\color{Red}
  We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
  }
\end{itemize}

### 2021-11-19 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
final corrections to paper res

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions. This is not an overly restrictive assumption and others have used the same assumption in their work, e.g. see \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

The paper is organized as follows. Sec.  \ref{sec:schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec:floquet_theory} provides the Floquet theory interpretation of these wave functions.
We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec. \ref{sec:inverse_scattering_time}, and use it in Sec. \ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}. {\color{Red}In Sec. \ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
Finally, we summarize our findings and present our conclusions in Sec. \ref{sec:conclusions}.}
%===============================================================================

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
The applied gate voltage to the system modifies the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}

@@

Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig.~\ref{fig:5} that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

>>>>

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions. These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g. see Endo \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

The paper is organized as follows. Sec.  \ref{sec:schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec:floquet_theory} provides the Floquet theory interpretation of these wave functions.
We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec. \ref{sec:inverse_scattering_time}, and use it in Sec. \ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}. {\color{Red}In Sec. \ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
Finally, we summarize our findings and present our conclusions in Sec. \ref{sec:conclusions}.}
%===============================================================================

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
The gate voltage modifies the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}

@@

Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig.~\ref{fig:5} that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
